ESRC SDAI Application

### 2019-06-12 case_for_support.tex
Wednesday

	unreported abuse / reported abuse ~ 
	[demographics] age + sex + marital status + earnings + ... 
	other crime dummies + ...
	[information about abuse] level of harm + ...
	[geomatched stuff] socioeconomic status

@@

Regression 2: 
	no abuse / abuse ~ 	[demographics] age + sex + marital status + earnings + employment + ... other crime dummies
		health + mental health +

@@

@@

>>>>

	abuse or not ~
   	[demographics] age + sex + marital status + earnings + ...
	other crime dummies + ...

	unreported abuse / reported abuse ~ 
	[demographics] age + sex + marital status + earnings + ... 
	other crime dummies + ...
	[information about abuse] level of harm + ...

@@

We can describe who is abused and their demographics in CSEW, CSEW who report, and in WMP.

We can also compare those abused in WMP data with any other reference group in the WMP data. (e.g., burgled) and then use DA-burgled in CSEW vs WMP to back out stuff.

@@

Should you be identifying the couples most at risk of serious harm from time-invariant properties, or should you be following couples over time and using time-varying properties to spot when to intervene?

@@

matched in socieoconomic
